A new type of generalized, self-evolving and efficient automated deduction algorithm based on category theory

### 2022-10-04 paper.tex
fix ref style

%% \special{dvipdfmx:config z 0} %% speed boost

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing
\usepackage{url}	%% for reference 9

\usetikzlibrary{positioning, cd, arrows}	%% for comutative diagram & flowchart drawing

@@

%% \setlength{\parskip}{0.8em}	%% set white space between paragraphs

\doublespacing

\begin{document}

\begin{frontmatter}
	\title{A new type of automated deduction algorithm based on category theory}

	\author[1]{Shao Xinhui\corref{cor1}}
	\ead{shaoxinhui@mail.neu.edu.cn}

	\author[2]{Zijian Wang\fnref{fn2}}
	\ead{felix_wzj@yahoo.com}
	\ead[url]{zijianfelixwang.github.io}

	\cortext[cor1]{Corresponding author, guiding the first author through the process of the research, professor of the Northerneastern University.}

	\fntext[fn2]{Author conducting the research, student of the Northeast Yucai School of P.R.China}

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},addressline={Department of Mathematics, College of Sciences, Northerneastern University},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given. The AMS codes are 03B35, 68V15, 18-00, 18-04, 68W99.
	\end{abstract}

	\begin{graphicalabstract}
		\begin{figure}[h]
			\begin{tikzpicture}[commutative diagrams/every diagram]
				\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
				\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
				\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
				\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
				\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

				\path[commutative diagrams/.cd, every arrow, every label, dashed]
				(K3) edge node {$K_3$} (Kn)
				(Kn) edge node {} (K1)
				(Kn) edge node {$k_N$} (K0);
			\end{tikzpicture}
		\end{figure}
	\end{graphicalabstract}

	\begin{keyword}
		automatic prover \sep theorem prover \sep algorithm \sep category theory \sep automatic deduction \sep automatic reasoning
	\end{keyword}
\end{frontmatter}

@@

\begin{figure}[h!t]
	\centering
	\begin{tikzpicture}[>=latex', font={\sf \small}]
		\def\smbwd{1cm}

@@

Additionally, I had few knowledge about \LaTeX before writing this paper. The $lshort$ documentation and the \TeX Stack Exchange helped me a lot. Here I express my genuine thankfulness to the online resources and documentation of the used \LaTeX packages and software components. This research did not receive any specific grant from funding agencies in the public, commercial, or
not-for-profit sectors.

\bibliographystyle{elsarticle-num}
\bibliography{paper}

\end{document}

>>>>

%% \special{dvipdfmx:config z 0} %% speed boost
\usepackage{txfonts, verbatim}
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing
\usepackage{url}	%% for reference 9
\usepackage[pagewise]{lineno}\linenumbers
\usepackage[comma, square, sort, numbers]{natbib}

\usetikzlibrary{positioning, cd, arrows, celtic}	%% for comutative diagram & flowchart drawing

\renewcommand{\bibnumfmt}[1]{[#1]}

\def\typeofarticle{}
\def\currentvolume{}
\def\currentissue{}
\def\currentyear{}
\def\currentmonth{}
\def\ppages{}
\def\DOI{}
\def\Received{}
\def\Revised{}
\def\Accepted{}
\def\Published{}

\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}
\makeatletter
\renewcommand{\@biblabel}[1]{#1\hfill \hspace{-0.2cm}}
\makeatother

\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

@@

%\pdfminorversion=7

%\bibliographystyle{unsrt}

\begin{document}
	\title{A new type of generalized, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Shao Xinhui\affil{1}\corrauth
		Zijian Wang\affil{2}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China}
		\addr{\affilnum{2}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China}
		\corraddr{shaoxinhui@mail.neu.edu.cn}
	}

	\begin{abstract}
	In this article a new type of generalized, self-evolving and efficient automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets structure provides an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given and examined for performance.
	\end{abstract}

	\keywords{
		\textbf{automatic prover, theorem prover, algorithm, category theory, automatic deduction, automatic reasoning}
		\newline
		\textbf{Mathematics Subject Classification:} 03B35, 68V15, 18-00, 18-04, 68W99
	}

	\maketitle

@@

	\begin{figure}[ht]
		\centering
		\begin{tikzpicture}[>=latex', font={\sf \small}]
			\def\smbwd{1cm}

@@

	Additionally, I had few knowledge about \LaTeX before writing this paper. The $lshort$ documentation and the \TeX Stack Exchange helped me a lot. Here I express my genuine thankfulness to the online resources and documentation of the used \LaTeX packages and software components.

	\section*{Conflict of interests}
	This research did not receive any specific grant from funding agencies in the public, commercial, or
	not-for-profit sectors.

%	\bibliography{paper}
	\bibliographystyle{unsrtnat}
	\bibliography{paper}
\end{document}
